---
title: "Telegram integration"
output: html_notebook
---

**Step 1** Create a telegram bot
To do so, follow steps [here](https://core.telegram.org/bots#6-botfather)

**Step 2** Find your chat ID
To make it work, you'll need an access TOKEN (it should look something like `123456:ABC-DEF1234ghIkl-zyx57W2v1u123ew11`). The next step is to find your chat ID. Open your bot in Telegram and hit `\start`. Now run the following code:

```{r}
# Initialize bot
token = 'my token goes here'
bot <- Bot(token = token)

# Retrieve your chat id
# Note: you should text the bot before calling `getUpdates` (you do this by running \start)
chat_id = bot$getUpdates()[[1L]]$from_chat_id()

print(chat_id) # Note this down
```

**Step 3** Run hpc with live Telegram updates


```{r}
host = 'myHostNameGoesHere'
overwrite_default = list(
  telegram = list(
    token = 'my Telegram token goes here',
    chat_id = 'my Chat bot chat ID goes here'
    # Optionally you can set the following parameters:
    # output_types = c('print', 'message'), # this are statements in your code, that are redirected to Telegram
    # redirect_print = T, # if this is true the statements are redirected
    # send_on_start = T, # Send a message when the script starts
    # send_on_finish = T, # Send a message when the script ends
    # silence_unimportant_msg = T # Warnings, messages or simple print messages are sent silently, so you'll receive no alert
  )
)
connect(host, overwrite_default)
```

**Step 4** Send files to Telegram

If you run a function on your server you can also send files to Telegram, for example a plot of your code

```{r}
my_telegram_function = function(){
  telegram_upload_file('my_plot.pdf')
}

hpc_run(settings, my_telegram_function, list())
```

