---
title: "Setting up SSH"
output: html_notebook
---

In order to use the package you'll need ssh access with `R` installed on the server. Sometimes on hpc you can't directly ssh into your workspace, but need to chain ssh sessions. Chaining ssh sessions within the package `ssh` is not possible. This is a `R`-package we use in order to work with R over ssh. To go around this issue we'll first build a tunnel and use this instead.

Let's imagine the following scenario, you have your own computer (`hostA`), you can connect to your workspace on the cluster (`hostB`) and only from your workspace you can connect to the hpc cluster (`hostC`). In order to setup the tunnel `hostA -> hostB -> hostC`, we'll need to do the following:

**Step 1** Create the file `config`

Type this into your terminal
```{r}
nano ~/.ssh/config
```

In many cases this file does not exist yet. 

**Step 2** Add and edit the following lines to your configuration

```{r}
Host hostC # You could pick any name, e.g. 'Host hpc_server'
    HostName hostC # The host name of hostC
    User username_hostC # The username for hostC
    IdentityFile ~/.ssh/id_rsa # We'll get to this in a sec
    ProxyCommand ssh username_hostB@hostB -W %h:%p # this is where the magic happens ;-) You first login to hostB and then into hostC
```

**Step 3** Create a keygen for ssh
This step is optional, but if you don't want to use it, you'll need to remove the IdentityFile line from the config file. However, I strongly recommend to put your ssh password into the keygen. If you want to do so paste this into the terminal

```{r}
ssh-keygen -t rsa -b 2048 # This creates a keygen for ssh (rsa protected)
```

Automatically the keygen is saved in `~/.ssh/id_rsa`, however you may use any other location. Please not that, you'll need to change the location of `IdentityFile` in `~/.ssh/config`). Next, you'll be prompted to enter a password, if you just press enter, no password is used. I recommend this for scripting, because otherwise you'll need to reenter your ssh keygen password each time you run.

**Step 4** Add ssh to keygen
In order to add the ssh key to the keygen run:

```{r}
ssh-copy-id username_hostB@hostB
```

**Step 5** Launch tunnel
You may either setup a tunnel using a terminal, by entering:

```{r}
ssh -L 5902:localhost:22 -N hostC
```

Or you use the build in tunnel management in `hpcR`. You can easily do so by

```{r}
library(hpcR)
host = 'username_hostB@localhost:5902' # hostname
overwrite_default = list(
  tunnel = list(
    executable = '/usr/bin/ssh', # path to the ssh executable
    args = c('-L', '5902:localhost:22', '-N', 'hostC'), # arguments to setup the tunnel
    timeout = 1 # if it could not connect, it will try again in 1 second
  )
)
```

Both versions of the same code connect `localhost` on port 5902 to `hostC` on port 22. The hostname you'll need to use in this package is therefore `username_hostB@localhost:5902`



