---
title: "Using SLURM"
output:
  html_document:
    df_print: paged
---

This implementation of SLURM has two operation modes: execute the whole function on the cluster or parallelize the code on the server.

```{r}
# Dummy data
df = data.frame(a = 1:20, b = 21:40)

multiply = function(df){
  products = c()
  for (i in 1:nrow(df)){
    products = c(products, df[i, 1]*df[i, 2])
  }
  return(products)
}

result_normal = multiply(df)
```


**Execute whole function on cluster**
```{r}
# Do it the slurm way
host = 'myHostNameGoesHere'
overwrite_default = list(
  slurm = list(
    enabled = T,
    mode = 'single',
  )
)

settings = connect(host, overwrite_default)
sjob = run_hpc(settings, multiply, list(df = df))
Sys.sleep(10) # Wait for SLURM to finish
result_slurm = receive_output(settings, sjob) # grab the result

if(!identical(result_slurm, result_normal)){
  stop('Slurm and normal way give different results')
}
disconnect(settings)
```

**Run in parallel on cluster**
We can do the same, but now in parallel:

```{r}
overwrite_default$slurm$mode = 'parallel' # change 'single' to 'parallel'
settings = connect(host, overwrite_default)

# We'll need to adapt the function a bit for parallization
multiply_row_wise = function(a, b){
  return(a*b)
}

sjob_parallel = run_hpc(settings, multiply_row_wise, list(df = df))
Sys.sleep(10)
result_slurm_parallel = unlist(receive_output(settings, sjob_parallel))
if(!identical(result_slurm_parallel, result_normal)){
  stop('Slurm and normal way give different results')
}
disconnect(settings)
```

**More settings**
Here I show some more advanced settings. If you want to use `rscript_path` please use `rslurm` from [here](https://github.com/polvanrijn/rslurm) or run `devtools:install_github("polvanrijn/rslurm")` on the hpc cluster.

```{r}
overwrite_default = list(
  slurm = list(
    enabled = T,
    mode = 'single',
    nodes = 8, # number of nodes
    cpus_per_node = 32, # num of cpus per node
    options = list(
      partition = 'name_of_partition_you_want_to_use'
    ),
    rscript_path = 'my/custom/path/to/Rscript'
  )
)
```


